\documentclass{ExpressiveCoverLetter}

\usepackage{lipsum}
\usepackage{setspace}


\begin{document}

\coverletterheader[
    firstname=Justin,
    middleinitial=B,
    lastname=Napolitano, 
    email=justin@jnapolitano.io, 
    phone=832-299-0372,            
    city=Houston,
    state=Texas
]

%\vspace{0.25in}

Nico Janssen, 

\begin{flushleft}
\begin{normalsize} 

    \singlespacing 

    Thank you for accepting my request to write you.  
			
    As I mentioned, I am struggling to find a role that is the right fit for me.  
    
    I studied political science with a statistics concentration.  As an undergraduate, I worked as a research assistant on two projects.  I also completed two undergraduate thesis papers. 

    The first project entailed working with Dr. Demet Mousseau to record the history of human right abuses commited in the Kurdish-Turkish Conflict. We developed the Turkish Kurdish Analysis Database; presented at the Peace Science Conference in 2019 and published in the Journal of Peace Economics, Peace Science and Public Policy.  You may find the DOI link at \href{https://doi.org/10.1515/peps-2019-0036}{https://doi.org/10.1515/peps-2019-0036}. My role was to develop the research methodology, maintain a noSQL database, integrate data, and perform analysis.  The documentation may be found \href{https://journal.jnapolitano.io/parts/articles/project-kurdish-conflict/index.html}{at the following link: https://journal.jnapolitano.io}

    I also worked with Dr. Thomas Dolan to produce a sentiment analysis report of the Blair Government's dialogue regarding the invasion of Iraq.  We integrated data produced by research assistants to determine if the emotional state of MP's correlated with the final vote to engage in the Iraq War. The analysis was included in the following paper: \href{https://www.journals.uchicago.edu/doi/10.1086/691200}{https://www.journals.uchicago.edu/doi/10.1086/691200}.   
    
    Dr. Thomas Dolan later advised me on my first independent research project.  I reviewed the history of the transition of the GATT to the WTO.  The primary intent of the research was to better understand the role of the wealthiest states in determining the outcomes of international agreements.  In short, we concluded that the G7 determines the allocation of resources.  A sample of that paper can be found at \href{https://journal.jnapolitano.io/parts/articles/project-evolution-of-ngos/index.html}{https://journal.jnapolitano.io}.
    
    Dr. Drew Lanier also instructed me in an analysis of the public accomodation case law and the empirical analysis of judicial voting behavior in the \href{https://www.law.cornell.edu/supremecourt/text/16-111}{Masterpiece Cake vs. Colorado Civil Rights Commission Supreme Court case}.  You may find this paper at \href{https://journal.jnapolitano.io/parts/articles/project-supcourt-masterpiececake/index.html}{https://journal.jnapolitano.io}.

    Following completion of my undergraduate degree in 2018, I studied computational statistics courses at the master's level for a year to supplement my work in the Kurdish-Turkish Data Base and to prepare for a master's program in international political economy at the Korbel School of the University of Denver.  

    In August of 2019, I was diagnosed with a rare form of Leukemia.  I succesfully underwent curative treatment at MD Anderson Cancer Center in Houston, Texas.

    I could not work full time or pursue my education during this period of my life.  I founded Napolitano-Tseng at this time in order to remotely contract as a data base developer and a marketing analyst.  I leveraged my statistical and data oriented expertise to create analytic workflows that automated data collection for two firms.  Frankly, I did not enjoy this type of work.  

    I finished treatment in January of 2022.  I have since struggled to market myself.  I do not want to work in the business analytics field. Nor do I want to build data infrastructure used to market products.  I would like to ideally transition back into a research role.  Unfortunately, I am not a candidate for these positions as I could not complete a master's degree.  

    Currently, I am seeking a role that would enable me to work on initiatives that are meaningful.  I would also like to be able pursue a master's degree within a year or two.  

    I am hopeful that you may be able to recommend a suitable next step for me as I transition back in to the work force.

    \vspace{.15in}

    Sincerely,

    \vspace{.15in}

    Justin Napolitano

\end{normalsize}
\end{flushleft}

\end{document}