\documentclass{ExpressiveCoverLetter}

\usepackage{lipsum}
\usepackage{setspace}


\begin{document}

\coverletterheader[
    firstname=Justin,
    middleinitial=B,
    lastname=Napolitano, 
    email=justin@jnapolitano.io, 
    phone=832-299-0372,            
    city=Houston,
    state=Texas
]

%\vspace{0.25in}

NRG Energy,

\begin{flushleft}
\begin{normalsize} 

    \singlespacing 

    I am a quantitative analyst experienced with Python, SAS, and the Julia computing languages seeking a energy market analyst position.
    
    I studied political science with a statistics concentration.  As an undergraduate, I worked as a research assistant on two projects.  I also completed two undergraduate thesis papers. 

    Dr. Demet Mousseau and I recorded the history of human right abuses commited in the Kurdish-Turkish Conflict. We developed the Turkish Kurdish Analysis Database which was presented at the Peace Science Conference in 2019 and published in the Journal of Peace Economics, Peace Science and Public Policy.  My role was to develop the research methodology, maintain a noSQL database, integrate data, and perform analysis.  The documentation may be found \href{https://journal.jnapolitano.io/parts/articles/project-kurdish-conflict/index.html}{at the following link: https://journal.jnapolitano.io}

    I also worked with Dr. Thomas Dolan to produce a sentiment analysis report of the Blair Government's dialogue regarding the invasion of Iraq.  The analysis was included in the following paper: \href{https://www.journals.uchicago.edu/doi/10.1086/691200}{https://www.journals.uchicago.edu/doi/10.1086/691200}.   
    
    Dr. Thomas Dolan later advised me in the review of the transition of the GATT to the WTO.  The primary intent of the research was to better understand the role of the wealthiest states in determining the outcomes of international agreements.  A sample of that paper can be found at \href{https://journal.jnapolitano.io/parts/articles/project-evolution-of-ngos/index.html}{https://journal.jnapolitano.io}.
    
    Dr. Drew Lanier also instructed me in the statistical analysis of judicial voting behavior in the \href{https://www.law.cornell.edu/supremecourt/text/16-111}{Masterpiece Cake vs. Colorado Civil Rights Commission Supreme Court case}.  You may find this paper at \href{https://journal.jnapolitano.io/parts/articles/project-supcourt-masterpiececake/index.html}{https://journal.jnapolitano.io}.

    Following completion of my undergraduate degree in 2018, I studied computational statistics courses at the master's level for a year to supplement my work in the Kurdish-Turkish Data Base and to prepare for a master's program in international political economy at the Korbel School of the University of Denver.  

    In August of 2019, I was diagnosed with a rare form of Leukemia.  I succesfully underwent curative treatment at MD Anderson Cancer Center in Houston, Texas.

    I founded Napolitano-Tseng at this time in order to remotely contract as a data base developer and a marketing analyst.  I leveraged my statistical and technical expertise to create analytic workflows that automated data collection for two firms.

    I completed treatment in January of 2022.  Currently, I am seeking a role that would enable me to work on initiatives that are meaningful.  I would also like to be able pursue a master's degree within a year or two.  

    \vspace{.15in}

    Sincerely,

    \vspace{.15in}

    Justin Napolitano

\end{normalsize}
\end{flushleft}

\end{document}