\documentclass{ExpressiveCoverLetter}

\usepackage{lipsum}
\usepackage{setspace}


\begin{document}

\coverletterheader[
    firstname=Justin,
    middleinitial=B,
    lastname=Napolitano, 
    email=justin@jnapolitano.io, 
    phone=832-299-0372,            
    city=Houston,
    state=Texas
]

%\vspace{0.25in}

Mr. Navinskey,

\begin{flushleft}
\begin{normalsize} 

    \singlespacing 

    I am a quantitative analyst experienced with the Python, SAS, and the Julia computing languages seeking a data centric analyst position.
    
    I studied political science with a statistics concentration.  I also studied computational statistics at the master's level to supplement my role as a research professional.  My achievements include publishing an analysis of human rights abuses presented at the Hague, managing the data integration pipelines for a meta-analysis of war and public policy, and founding a marketing analytics firm.  

    I am most proud of the Turkish Kurdish Analysis Database which was presented at the Peace Science Conference in 2019 and published in the Journal of Peace Economics, Peace Science and Public Policy.  My role was to develop the experimental design, maintain a noSQL database, integrate data from open source intelligence sources, and to perform statistical analysis.  The documentation may be found \href{https://journal.jnapolitano.io/parts/articles/project-kurdish-conflict/index.html}{at the following link: https://journal.jnapolitano.io}

    I also designed the research methodology, managed the data integration, and ensured the validity of data produce by a team of research assistants in a sentiment analysis of politicians during times of war.  The report included a review of 13 nations to determine the effect of public opinion on elected officials.  Final analysis was included in the following paper: \href{https://www.journals.uchicago.edu/doi/10.1086/691200}{www.journals.uchicago.edu/doi/10.1086/691200}.   

    Leveraging my statistical and research background, I founded Napolitano-Tseng to improve the data analytics infrastructure for marketing teams.  I transitioned two firms from Excel and SQL based workflows to scalable cloud infrastructure based on graph databases and automated data extraction, transformation, and loading procedures.  I decided to transition away from this company in January of 2022 to focus on developing myself as an analyst and research professional.  
    
    In my spare time, I independently publish analytical research articles relating to supply chains, the energy infrastructure, and public policy at \href{https://blog.jnapolitano.io}{blog.jnapolitano.io} and on my LinkedIn profile: \href{https://www.linkedin.com/in/justin-napolitano/}{in/justin-napolitano}. My work includes \href{https://freight.jnapolitano.io}{a meta-analysis of the entire North American freight network}; and \href{https://blog.jnapolitano.io/carbon-shipping-projections/}{a shipping projection article simulating the transport of captured carbon between European and American ports to determine the annual and per voyage economic scale of this market}. 

    Please consider my application.  I would be a good fit for any team in need of an analyst with technical ability, research experience, and the ability to translate findings to actionable business insights. 

    \vspace{.15in}

    Sincerely,

    \vspace{.15in}

    Justin Napolitano

\end{normalsize}
\end{flushleft}

\end{document}